---
title: "Financial Econometrics: Problem Set 1"
author:
- Rebecca Cardebring
- Kazi Jahurul Islam
- Jack (Quan Cheng) Xie
date: "January 2023"
output:
  pdf_document: default
---

```{r setup, include=FALSE}
library(FE) # course package

library(tidyverse) # plot
library(psych) # summary

library(knitr) # for tables
opts_chunk$set(echo = F) # do not show code

library(kableExtra)

```

## A. Distributional properties of Dow Jones index returns

The Dow Jones Industrial Average (DJIA) is a stock market index of 30 prominent companies listed on stock exchanges in the United States and one of the oldest and most commonly followed equity indexes. In this section we examine the statistical properties of DJIA.

```{r plotDJ}

daily <- DJ_d$r_Dow_Jones
weekly <- DJ_w$r_close

# par(mfcol=c(2, 1))

fig.dim = c(6, 3)

plot(daily, type = 'l', main = 'DOW Daily Returns',
     xlab = 'Time Horizon', ylab = 'Log Return')


plot(weekly, type = 'l', main = 'DOW Weekly Returns', 
     xlab = 'Time Horizon', ylab = 'Log return')

```

### 1. DOW Jones Descriptive Statistics

```{r distrib prop}

desc_daily <- data.frame(describe(DJ_d$r_Dow_Jones), row.names = "Daily")
desc_weekly <- data.frame(describe(DJ_w$r_close), row.names = "Weekly")

descr <- t(rbind.data.frame(desc_daily, desc_weekly))

# show only selective statistics
descr <- descr[c("n", "mean", "sd", "median", "min", "max", "skew", "kurtosis"), ]

rownames(descr) <- c("Observations", "Mean", "Standard Deviation",
                   "Median", "Min", "Max",
                   "Skewness", "Kurtosis")

kbl(descr, digits=3, booktabs=T, caption = 'Dow Jones Index Returns Descriptive Statistics')
```

### 2. Empirical Distributional of Log Returns

```{r qq_normal, out.width="90%"}

# standardize first and second moments with standard normal
std_daily = (daily - mean(daily)) / sd(daily)
std_weekly = (weekly - mean(weekly)) / sd(weekly)

# plot qq
par(mfcol=c(1, 2)) # plot side-by-side

qqnorm(std_daily, main = c("Normal Q-Q Plot:", "Daily Log Returns"))
qqline(std_daily, col = "red")

qqnorm(std_weekly, main = c("Normal Q-Q Plot:", "Weekly Log Returns"))
qqline(std_weekly, col = "red")
```

```{r qq_tdist, out.width="90%"}

# need 2 parameters to normalize the data (mean and std dev)
df = 3

# standardize data
std_daily_t = std_daily * sqrt(df / (df-2))
std_weekly_t = std_weekly * sqrt(df / (df-2))

# plot qq
par(mfcol=c(1, 2)) # plot side-by-side

qqplot(rt(length(std_daily_t), df = df),
       std_daily_t,
       main = c("T-distribution Q-Q Plot:", "Daily Log Returns"),
       xlab = "Theoretical quantiles",
       ylab = "Sample quantiles"
       )

qqline(std_daily_t, col = "red")

qqplot(rt(length(std_weekly_t), df = df),
       std_weekly_t,
       main = c("T-distribution Q-Q Plot:", "Weekly Log Returns"),
       xlab = "Theoretical Quantiles",
       ylab = "Sample Quantiles"
       )

qqline(std_weekly_t, col = "red")
```

### 3. Distributional Goodness-of-fit Tests

```{r chi-test normal}

test_fit <- function(data,
                     r_theoretical, # theoretical cdf, e.g. pnrom, pt
                     b=30 # number of quantile bins
                     ){
  
  # divide quantile bins equally
  bin = 1:b/b
  
  # vector of quantiles
  vq = NULL; for(val in bin) vq = c(vq, sum(r_theoretical <= val)) 
  vq = c(vq[1], diff(vq))
  
  # calculate chi-squared stat and p-value
  chi_test = sum((vq-length(data)/b)**2 / (length(data) / b))
  pval = 1 - pchisq(chi_test, df = b - 3)
  
  return(list(test=chi_test, pval=pval))
  
}

df = 4

dimnames <- list(c('Daily', 'Weekly'),
                 c('Normal', 'Student t (df=4)', 'Mixed normal'))

# result tables
tab <- matrix(nrow=2, ncol=3, dimnames=dimnames)
tab.p <- matrix(nrow=2, ncol=3, dimnames=dimnames)

# test with normal
fit_daily = test_fit(std_daily, pnorm(std_daily))
fit_weekly = test_fit(std_weekly, pnorm(std_weekly))

tab[1, 1] <- fit_daily$test
tab.p[1, 1] <- fit_daily$pval

tab[2, 1] <- fit_weekly$test
tab.p[2, 1] <- fit_weekly$pval

# test with t-distribution
fit_daily = test_fit(std_daily_t, pt(std_daily_t, df=df))
fit_weekly = test_fit(std_weekly_t, pt(std_weekly_t, df=df))

tab[1, 2] <- fit_daily$test
tab.p[1, 2] <- fit_daily$pval

tab[2, 2] <- fit_weekly$test
tab.p[2, 2] <- fit_weekly$pval

# test with mixed normal


# show table

kbl(tab, booktabs=T, digits=5, caption='Goodness-of-fit: Chi-square test statistic')
kbl(tab.p, booktabs=T, digits=5, caption='Goodness-of-fit: p-value')

```

## B. Dynamic properties of financial return series

Please see below for some summary statistics of the international stock indexes.

```{r, results='asis'}
# generate log returns
lret = apply(log(index_d), 2, diff)
# summarize data
descr <- describe(lret)
descr <- descr[, c("n", "mean", "sd", "median", "min", "max", "skew", "kurtosis")]

colnames(descr) <- c("Obs.", "Mean", "Std Dev", "Median", "Min", "Max", "Skew", "Kurt")

kbl(descr, caption='Summary Statistics of Daily Index Returns',
    digits=5, booktabs=T)
```

### 1. Autocorrelation of international stock indexes

```{r acf_pacf, results='asis'}
acf_tabs <- function(data, lag.max=20, plot=T){
  # create tables for ACF and PACF values
  acf_tab <- matrix(nrow=ncol(data), ncol=lag.max,
                    dimnames=list(index=colnames(data),
                                  lag=1:lag.max
                    )
  )
  pacf_tab <- matrix(nrow=ncol(data), ncol=lag.max,
                     dimnames=list(index=colnames(data),
                                   lag=1:lag.max)
  )
  
  for (c in colnames(data)){
    # data for each column removing na
    x <- data[!is.na(data[,c]), c]
    
    if (plot){
    # two columns for ACF and PACF
    par(mfcol=c(1, 2))
    }
    
    # plot ACf and PACF
    acf_val <- acf(x, main=c, plot=plot)
    pacf_val <- pacf(x, main=c, plot=plot)
    # save coefficients
    acf_tab[c, ] <- acf_val$acf[2:(lag.max+1)]
    pacf_tab[c, ] <- pacf_val$acf[1:lag.max]
  }
  return(list(acf=acf_tab, pacf=pacf_tab))
}
tabs = acf_tabs(lret)
# xtable(t(tabs$acf))
# xtable(t(tabs$pacf))
kbl(t(tabs$acf), digits=5, booktabs=T)
kbl(t(tabs$pacf), digits=5, booktabs=T)
```

### 2. Ljung-Box Tests

```{r ljungbox, results='asis'}

# Ljung-Box test function
LB <- function(data, lag, p){
  # time periods
  T <- length(data)
  # get ACF coeffs
  rho = acf(data, lag.max=lag, plot=F)$acf
  # remove 0th lag coeffs then square
  rho_sq = rho[2:(lag+1)]**2
  # test statistic
  Q = T * (T+2) * sum(rho_sq / (T-1:lag))
  # return test and p-value
  return(list(test=Q, pval=1-pchisq(Q, df=lag-p)))
}

# lag periods to test
lags <- c(10, 50, 100)


p <- 0

# generate table of Ljung-Box test results
LB_tab <- function(data,
                   lags = c(10, 50, 100),
                   p = 0 # degrees of freedom df = lag - p, where p is number of parameters estimated
                   ){
  # table of LB test statistics
  LB_tests <- matrix(nrow=length(lags), ncol=ncol(data),
                    dimnames=list(lag=lags, index=colnames(data))
                    )
  
  # table of Chi-square test p-values
  LB_pvals <- matrix(nrow=length(lags), ncol=ncol(data),
                     dimnames=list(lag=lags, index=colnames(data))
                     )
  
  # run Ljung-Box tests
  for (c in colnames(data)){
    for (i in 1:3){
      # remove na from data
      x <- data[!is.na(data[,c]), c]
      LB_res <- LB(x, lag=lags[i], p)
      # significance level stars
      pval <- signif(LB_res$pval, 3)
      for (qt in c(0.1, 0.05, 0.01)){
        if (LB_res$pval < qt){
          pval <- paste(pval,'*', sep='')
        }
      }
      # save test stat and pvals
      LB_tests[i, c] <- LB_res$test
      LB_pvals[i, c] <- pval
    }
  }
  return(list(test=LB_tests, pvals=LB_pvals))
}


tab <- LB_tab(lret)

kbl(tab$pvals, booktabs=T, caption = "Ljung-Box Test p-values") %>%
  kable_classic() %>%
  add_footnote(
    c('This table presents p-values of Ljung-Box tests of no autocorrelation.',
      'Significance levels: *p-value < 0.1, ** p-value < 0.5, *** p-value <0.01.'),
    notation="none")
```

### 3. Cross-correlations

```{r crosscor}
corr_mat <- function(data, lag=1) {
  # column names
  cols <- colnames(data)
  # correlation matrix
  corr_mat <- matrix(nrow = ncol(data), ncol = ncol(data),
                     dimnames=list(lags=cols, cols))
  for (c1 in cols){
    for (c0 in cols){
      # periods with either are NA
      isna <- (is.na(data[, c1]) | is.na(data[, c0]))
      # non-na returns of pair
      pair_data <- data[!isna, c(c1, c0)]
      T <- nrow(pair_data)
      # add period lag autocorrelation to matrix
      corr_mat[c1, c0] <- cor(pair_data[1:(T-lag),c1], pair_data[(1+lag):T,c0])
      # acf(pair_data)
      # pacf(pair_data)
    }
  }
  # re-label past/current period returns
  # rownames(corr_mat) <- paste(cols, '(t-1)', sep='')
  # colnames(corr_mat) <- paste(cols, '(t)', sep='')
  return(corr_mat)
}

ncols = length(colnames(lret))

kbl(corr_mat(lret, lag=0), caption = "Cross-correlations with Period $t$",
    booktabs = T, digits = 3) %>%
  add_header_above(c("", "Period t"=ncols)) %>%
  kable_styling(latex_options = c("repeat_header"))

kbl(corr_mat(lret, lag=0), caption = "Cross-correlations with Period $t-1$",
    booktabs = T, digits = 3) %>%
  add_header_above(c("", "Period t"=ncols)) %>%
  kable_styling(latex_options = c("repeat_header"))

```

### 4. Squared log returns

```{r sq_lret ACF}

# generate squared log returns
sq_lret = lret^2

# ACF and PACF
tabs = acf_tabs(sq_lret)

kbl(t(tabs$acf), booktabs=T)
kbl(t(tabs$pacf), booktabs=T)

```

```{r sq_lret LB}
# Ljung-Box test
tab <- LB_tab(sq_lret)

kbl(tab$pvals, booktabs=T,
    caption = "Ljung-Box Test p-values") %>%
  kable_classic() %>%
  add_footnote(
    c('This table presents p-values of Ljung-Box tests of no autocorrelation.',
      'Significance levels: *p-value < 0.1, ** p-value < 0.5, *** p-value <0.01.'),
    notation="none")
```

```{r sq_lret-crosscor}
ncols = length(colnames(lret))

kbl(corr_mat(sq_lret, lag=0), caption = "Cross-correlations with Period $t$",
    booktabs = T, digits = 3) %>%
  add_header_above(c("", "Period t"=ncols)) %>%
  kable_styling(latex_options = c("repeat_header"))

kbl(corr_mat(sq_lret, lag=0), caption = "Cross-correlations with Period $t-1$",
    booktabs = T, digits = 3) %>%
  add_header_above(c("", "Period t"=ncols)) %>%
  kable_styling(latex_options = c("repeat_header"))
```
