---
title: "Financial Econometrics: Problem Set 2"
author:
- Rebecca Cardebring
- Kazi Jahurul Islam
- Jack (Quan Cheng) Xie
date: "January 2023"
output:
  pdf_document:
    keep_tex: true
    df_print: kable
---

```{r setup, include=FALSE}
library(FE) # course package

library(tidyverse) # plot
library(psych) # summary

library(knitr)
opts_chunk$set(echo = FALSE)

library(kableExtra) # for latex tables
library(stargazer) # for regression tables
```

## 

# Part 1: Capital Asset Pricing Model

## A. Size and Book-to-Market Effects

### 1. Descriptive statistics of portfolios

***Analyze the descriptive statistics of the returns of the different portfolios. Do you find systematic differences in dependence of size and the book-to-market ratio?***

The following plots summarizes the descriptive statistics of size (ME) and book-to-market (MEBE) portfolios by deciles.

-   Size deciles downward trending in all measures.

-   Book-to-market deciles upward trending.

```{r}


# describe portfolio
descr <- describe(portfolio_m)

descr <- descr[, c("n", "mean", "sd", "median", "min", "max", "skew", "kurtosis")]

colnames(descr) <- c("Observations", "Mean", "StdDev",
                   "Median", "Min", "Max",
                   "Skewness", "Kurtosis")
```

```{r}

# TODO:
# common x/y axes
# column and row titles

layout(mat = matrix(c(1:8), nrow=4, ncol=2),
       heights = rep(2, 4), # Heights of the two rows
       widths = rep(2, 2)) # Widths of the two columns

# par(mfcol=c(4, 2))

# set margins
par(mar=c(4, 4, 0, 0))

# for market size and book-to-market ratio
for (lab in c("ME", "MEBE")){
  
  # plot descriptive statistics
  for (col in c("Mean", "StdDev", "Skewness", "Kurtosis")){
    
    # dev.new(width=2, height=1, unit="in")
    # variable names
    vars = NULL
    for(i in 1:10) vars = c(vars, paste(lab, i, sep=""))
    
    plot(descr[vars, c(col)],
         xlab = "Decile", ylab = paste(lab, col)
         )
  }
}
```

### 2. CAPM and Size and Book-to-Market Portfolios

***For all individual size and book-to-market portfolios as well as the market portfolio(s), compute the corresponding excess returns. Then, estimate the CAPM for selected portfolios and answer the following questions***

***(a) Test the validity of the CAPM for the individual size and book-to-market portfolios. Can you confirm the CAPM relationship across the cross-section of size and bookto-market portfolios?***

-   Plot excess returns (intercepts) and confidence bands (three different levels?).

-   Make excess returns table for Rxy x-th size and y-th book-to-market percentiles

-   If excess returns significantly different from zero then CAPM fails.

***(b) Is there a systematic relation between the estimated market beta and size as well as the book-to-market ratio? Interpret your findings.***

-   Plot confidence bands around betas

-   Beta is downward trending for size portfolios (big companies are less volatile) and upward trending for book-to-market (More volatile? Does this make sense?).

-   Check/plot significance levels.

**(c) Is there a systematic relation between the R\^2 and market capitalization as well as book-to-market ratio? What does this mean?**

-   R-square is upward trending for size. The bigger the size, the more the market explains variations in portfolio returns. Makes sense as larger companies make up more of the market.

-   R-square is largely constant across book-to-market deciles. Market explains less the larger MEBE portfolios.

```{r}

# variable names

# size column names
ME = NULL
for(i in 1:10) ME = c(ME, paste("ME", i, sep=""))

# book-to-market column names
MEBE = NULL
for(i in 1:10) MEBE = c(MEBE, paste("MEBE", i, sep=""))

# portfolio returns for x-th ME and y-th MEBE percentile
Rxy <- NULL
for(i in 1:10) for(j in 1:10) Rxy <- c(Rxy, paste("R", i, j, sep=""))

# list of market and portfolio column names
cols = c("Market", ME, MEBE, Rxy)

# risk-free rate
rf <- portfolio_m[, c("Tbill")]

# excess returns: gross returns minus risk-free
z <- portfolio_m[, cols]
z <- apply(z, 2, function(x) x - rf)
z <- data.frame(z)
colnames(z) <- cols

# time variables
tcols <- c("year", "month")
z[,tcols] <- portfolio_m[,tcols]

z <- z[, c(tcols, cols)]

ncols = length(cols)

tmp1 <- NULL
tmp2 <- NULL
tmp3 <- NULL
tmp4 <- NULL

# iterate through MEx, MEBEx, Rxy portfolios
for (col in cols[1:ncols]){
  
  # estimate
  model <- lm(data = z, formula = paste(col, "~ Market") )
  
  # get market beta
  tmp1 <- c(tmp1, model$coefficients["Market"])
  
  # excess returns
  tmp2 <- c(tmp2, model$coefficients["(Intercept)"])
  
  # get R-squared
  tmp3 <- c(tmp3, summary(model)$r.squared)
  
  # get adj. R-squared
  tmp4 <- c(tmp4, summary(model)$adj.r.squared)
}

# market beta
coeffs <- data.frame(list(
  "Decile" = 1:10, "ME" = tmp1[1:10], "MEBE" = tmp1[11:20]
  ), row.names = 1:10)

# excess returns
alpha <- data.frame(list(
  "Decile" = 1:10, "ME" = tmp2[1:10], "MEBE" = tmp2[11:20]
  ), row.names = 1:10)


# r-squared
r.sq <- data.frame(list(
  "Decile" = 1:10, "ME" = tmp3[1:10], "MEBE" = tmp3[11:20]
  ), row.names = 1:10)

```

```{r}

# table of coefficients
kbl(coeffs,
    digits=3, booktabs=T,
    caption = "Market Betas by Book-to-Market Ratio and Size Deciles")

# plot coefficients and R-squared
layout(mat = matrix(c(1:6), nrow=3, ncol=2),
       heights = rep(2, 4), # Heights of the two rows
       widths = rep(2, 2)) # Widths of the two columns

par(mar=c(4, 4, 0, 0))

for (lab in c("ME", "MEBE")){
  
  plot(alpha[, lab],
       xlab = paste(lab, "Decile"),
       ylab = "Alpha")
  
  plot(coeffs[, lab],
       xlab = paste(lab, "Decile"),
       ylab = "Market Beta")
  
  plot(r.sq[, lab],
       xlab = paste(lab, "Decile"),
       ylab = "R-squared")
}
```

### 3. Joint test of CAPM

**3. Estimate the CAPM jointly for the complete set of size portfolios, book-to-market portfolios as well as portfolios built on the intersections of size and book-to-market deciles. Test for joint significance of the intercept terms using the F-test.**

-   Need to redo this. Look up how to do joint F-test of intercepts.

```{r}
depvars <- cols[2:ncols] # dependent variables
formula = paste("cbind(", paste(depvars, collapse=", "), ") ~ Market")

model = lm(formula, data=z)

anova(model)
```

### 4. Period-Specific Betas

**4. Use the 100 portfolios built on the intersections of size and book-to-market deciles and divide the sample in appropriate sub-periods. Specify a CAPM which allows for period specific betas and intercept terms. Estimate the model for these portfolios.**

<https://en.wikipedia.org/wiki/Fama%E2%80%93MacBeth_regression>

**(a) Do you find statistically significant evidence for time-varying market betas and intercept terms?**

**(b) Analyze whether the inclusion of period-specific effects does increase the model's goodness-of-fit.**

**(c) Do you find for particular size and book-to-market portfolios stronger time variations in market betas than for others?**

```{r}

formula = paste("cbind(", paste(Rxy, collapse=", "), ") ~ Market")

years <- z['year']

preff <- years < 1960 # pre-Fama-French

# test before and after Fama-French paper
print("Pre-CAPM (< 1960)")
period = preff
model <- lm(formula, data = z[period, ])
print(anova(model))

summ = summary(model)
rsq <- NULL
for (m in summ) rsq <- c(rsq, m$r.squared)
cat("R-squared: mean", mean(rsq), "var", var(rsq), "\n")


print("Post-CAPM (> 1960)")
period = !preff
model <- lm(formula, data = z[period, ])
print(anova(model))

summ = summary(model)
rsq <- NULL
for (m in summ) rsq <- c(rsq, m$r.squared)
cat("R-squared: mean", mean(rsq), "var", var(rsq), "\n")


# start and end years
yend <- max(years) + 1
ybeg <- min(years)

yspan <- yend - ybeg # year span

# for divisions of 2, 5, and 9 years
for (div in c(2, 4, 8)){
  
  cat("\n\n",
      "===============",
      div, "equal partitions",
      "===============",
      "\n\n")
  
  pspan <- yspan / div # period span
  
  for (n in 1:div){
    
    # period beginning and end
    pbeg <- round(ybeg + (n-1) * pspan)
    pend <- round(ybeg + n * pspan)
    
    # period filter
    period <- (pbeg <= years) & (years < pend)
    

    cat("\n", sprintf(paste("(%d of %d)", pbeg, "to", pend), n, div), '- ')
    
    model <- lm(formula, data = z[period, ])
    print(anova(model))
    
    summ = summary(model)
    rsq <- NULL
    for (m in summ) rsq <- c(rsq, m$r.squared)
    cat("R-squared: mean", mean(rsq), "var", var(rsq), "\n")
  }
}
```

## B. Cross-sectional regressions

**Use the data set portfolio_m analyzed in the previous section. In the following you have to analyze the cross-sectional implications of the CAPM.**

### 1. Cross-sectional betas

**Write R code to implement the First Pass regression which computes the cross-section of market betas, and save them together with the period-specific excess returns. Apply the code to compute the betas for the 100 size-book-to-market portfolios. Using the results to analyze the following issues:**

Write a function to do the first pass and period specific.

**(a) Evaluate the cross-sectional distribution of the estimated betas. Test whether the average betas are significantly different from one. Interpret your findings.**

```{r}

formula = paste("cbind(", paste(Rxy, collapse=", "), ") ~ Market")

model = lm(formula, data=z)

anova(model)

summ <- summary(model)

beta_Rxy <- matrix(NA, nrow=10, ncol=10)

x = 1
y = 1
name <- paste("Response R", x, y, sep="")

for (x in 1:10) {
  for (y in 1:10) {
    name <- paste("Response R", x, y, sep="")
    
    s <- summ[[name]] # model summary
    beta_Rxy[x, y] <- s$coefficients["Market", "Estimate"]
  }
}

View(beta_Rxy)
```

**(b) Evaluate the cross-sectional distribution of the computed (time series) R\^2's. What can you learn from this analysis?**

**(c) Evaluate the relationship between average excess returns and market betas. What would you expect from economic theory and what do you find?**
