---
title: "PS1 No.1A Rebecca"
author: "Rebecca"
date: ""
output:
  html_document:
    df_print: paged
  df_print: kable
  pdf_document:
    keep_tex: yes
toc: no
---

```{r setup, include=FALSE}
library(tidyverse)
library(FE)
library(psych)
library(knitr)

daily <- DJ_d$r_Dow_Jones
weekly <- DJ_w$r_close
```

## Statistical Properties of Asset Returns
### Distributional properties of Dow Jones index returns
> 1)

The Dow Jones is a stock market index of 30 prominent companies listed on stock exchanges in the United States and one of the oldest and most commonly followed equity indexes. Due to several beneficial properties such as symmetry and time-additivity and the fact that they can be interpreted as continuously compunded returns, logarithmic returns of the Dow Jones are considered here. When plotted over time in Figure ???, the time series of daily log returns appears at first sight to be more stationary than non-stationary. One remarkable feature of the series is the larger variance between 1928-1940. This can probably be explained by the financial crisis that started in 1928 and after that, by the beginning of World War II. The same pattern can naturally also be observed for the weekly log returns (see Appendix).

```{r plot1A1.1, echo=F}
plot1A1.1 <- ggplot(data=DJ_d) + geom_line(aes(x=1:nrow(DJ_d), y=r_Dow_Jones)) +
  labs(x='Time horizon', y='Log return', title='Dow Jones daily log returns')
plot1A1.1 + theme_classic()
```

The distributional parameters of the time series show that 
Remarkable: high kurtosis, weekly is much more skewed
Add histograms?

#### Table of distributional parameters
```{r distrib prop, echo=F}
distr_daily <- data.frame(describe(DJ_d$r_Dow_Jones), row.names = "Daily")
distr_weekly <- data.frame(describe(DJ_w$r_close), row.names = "Weekly")

dat.df <- t(rbind.data.frame(distr_daily, distr_weekly))
kable(dat.df[c("n", "mean", "sd", "median", "min", "max", "skew", "kurtosis"), ])
```

> 2)

```{r qq normal, echo=F}
#daily
std_daily = (daily - mean(daily))/sd(daily) # standardize the daily return to st.norm distrib.
qqnorm(std_daily, main = "Normal Q-Q plot for daily log returns")
qqline(std_daily, col = "red")

#weekly
std_weekly = (weekly - mean(weekly))/sd(weekly)
qqnorm(std_weekly, main = "Normal Q-Q plot for weekly log returns")
qqline(std_weekly, col = "red")
```

```{r qq t daily, echo=F}
#daily
df = 3 # the lower the df the bigger the kurtosis
std_daily_t = std_daily*sqrt(df/(df-2))
qqplot(rt(length(std_daily_t), df = df), std_daily_t, ,  main = "T-distribution Q-Q plot for daily log returns", xlab = "Theoretical Quantiles", ylab = "Sample Quantiles")
qqline(std_daily_t, col = "red")
```

```{r qq t weekly, echo=F}
#weekly
df=3 #because we need two parameters to normalize the data (mean and std dev)
std_daily = (daily - mean(daily))/sd(daily)
std_weekly = (weekly - mean(weekly))/sd(weekly)
std_daily_t = std_daily*sqrt(df/(df-2))

std_weekly_t = std_weekly*sqrt(df/(df-2))
qqplot(rt(length(std_weekly_t), df = df), std_weekly_t,  main = "T-distribution Q-Q plot for weekly log returns", xlab = "Theoretical Quantiles", ylab = "Sample Quantiles")
qqline(std_weekly_t, col = "red")
```

None of the distributions fit well, the one that fits the best is the t distr. Even here, tails don't fit, point towards a distrib. with higher kurtosis. (put all QQ plots next to each other)

> 3)

```{r test normal, echo=F}

test_tab <- matrix(nrow=2, ncol=2)
rownames(test_tab) <- c('Daily', 'Weekly')
colnames(test_tab) <- c('Normal', 'Student t (df=4')


b = 30
bin = 1:b/b

#daily
r_nor = pnorm(std_daily)
#hist(r_nor, breaks = 50)

vn = NULL
for(val in bin) vn = c(vn,sum(r_nor <= val)) 
vn = c(vn[1],diff(vn))
chi_test = sum((vn-length(std_daily)/b)**2/(length(std_daily)/b))
cat("test =",chi_test," df =",b-3," p-value =",1-pchisq(chi_test,df=b-3))

test_tab[1, 1] <- chi_test

#weekly
r_nor_w = pnorm(std_weekly)
#hist(r_nor_w, breaks=50)

vn_w = NULL
for(val in bin) vn_w = c(vn_w,sum(r_nor_w <= val)) #try to compute the frequency for the bins
vn_w = c(vn_w[1],diff(vn_w)) # put 1st value because differencing (why?) loses the first observation; vector of probabilities?
chi_test_w = sum((vn_w-length(std_daily)/b)**2/(length(std_weekly)/b))
cat("test =",chi_test_w," df =",b-3," p-value =",1-pchisq(chi_test_w,df=b-3))

test_tab[2, 1] <- chi_test_w
```

Refer to Rosenblatt and show one histogram

```{r test t, echo=F}
df = 4

#daily
r_t = pt(std_daily_t,df=df)
#hist(r_t, breaks=50)
vt = NULL; for(val in bin) vt = c(vt,sum(vt <= val))
vt = c(vt[1],diff(vt))
test = sum((vt-length(std_daily_t)/b)**2/(length(std_daily_t)/b)) # he used the std. normal data, not for t-dist.
cat("test =",test," df =",b-3," p-value =",1-pchisq(test,df=b-3)) # p-value = 0, reject t distr.
#diff. output than his (df, test etc)
test_tab[1, 2] <- test

#weekly
r_t_w = pt(std_weekly_t,df=df)
#hist(r_t_w, breaks=50)
vt_w = NULL; for(val in bin) vt_w = c(vt_w,sum(vt_w <= val))
vt_w = c(vt[1],diff(vt_w))
test = sum((vt_w-length(std_weekly_t)/b)**2/(length(std_weekly_t)/b))
cat("test =",test," df =",b-3," p-value =",1-pchisq(test,df=b-3))

test_tab[2, 2] <- test
```

```{r test mix, echo=F}
#arbitrary choice
alpha = 0.4
sigma = 2.7 # this is the var of the second normal distr. and the first one is std_daily?

#daily
mix_daily = std_daily*sqrt((1-alpha) + alpha*sigma**2) #as data is std. and needs to be multiplied with var of mixed distr.
r_mix = (1-alpha)*pnorm(mix_daily) + alpha*pnorm(mix_daily,sd=sigma) #corresp. CDF of the mixture normal distr.
#hist(r_mix)
vn_mix = NULL; for(val in bin) vn_mix = c(vn_mix,sum(r_mix <= val))
vn_mix = c(vn_mix[1],diff(vn_mix))
test = sum((vn_mix-length(std_daily)/b)**2/(length(std_daily)/b))
cat("test =",test," df =",b-3," p-value =",1-pchisq(test,df=b-3))

#optimization daily
func <- function(vx){
  alpha = vx[1]
  sigma = vx[2]
  mix_daily_opt = std_daily*sqrt((1-alpha) + alpha*sigma**2)

  r_mix_opt = (1-alpha)*pnorm(mix_daily_opt) + alpha*pnorm(mix_daily_opt,sd=sigma)
  vn_mix_opt = NULL; for(val in bin) vn_mix_opt = c(vn_mix_opt,sum(r_mix_opt <= val))
  vn_mix_opt = c(vn_mix_opt[1],diff(vn_mix_opt))
  return(sum((vn_mix_opt-length(std_daily)/b)**2/(length(std_daily)/b)))
}

func(c(0.15,4))

res <- optim(par=c(0.1,4),fn=func,method="BFGS") # this is not cherry-picking, this is optimizing (similar to OLS)

res
1-pchisq(res$value,df=b-3)

#optimization weekly
func <- function(vx){
  alpha = vx[1]
  sigma = vx[2]
  mix_weekly_opt = std_weekly*sqrt((1-alpha) + alpha*sigma**2)

  r_mix_opt_w = (1-alpha)*pnorm(mix_weekly_opt) + alpha*pnorm(mix_weekly_opt,sd=sigma)
  vn_mix_opt_w = NULL; for(val in bin) vn_mix_opt_w = c(vn_mix_opt_w,sum(r_mix_opt_w <= val))
  vn_mix_opt_w = c(vn_mix_opt_w[1],diff(vn_mix_opt_w))
  return(sum((vn_mix_opt_w-length(std_weekly)/b)**2/(length(std_weekly)/b)))
}

func(c(0.15,4))

res <- optim(par=c(0.1,4),fn=func,method="BFGS")

#hist of optimal daily
alpha_opt_d=0.1212156
sigma_opt_d=4.1111241
mix_daily_opt_er = std_daily*sqrt((1-alpha_opt_d) + alpha_opt_d*sigma_opt_d**2)
r_mix_opt_er = (1-alpha_opt_d)*pnorm(mix_daily_opt_er) + alpha*pnorm(mix_daily_opt_er,sd=sigma_opt_d)
hist(r_mix_opt_er, breaks = 50, main = "Histogram of the optimal mixed normal distribution (2 components)")
```

Even when mixed, histogram npot unoformly distr. and p value too small.
