---
title: "Report for PS 1"
author:
- Jack Xie
date: ""
output:
  html_document:
    df_print: paged
    keep_tex: yes
  df_print: kable
  pdf_document:
    keep_tex: yes
toc: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(FE)
library(psych)
library(knitr)

library(xtable)
```

# Dynamic properties of financial return series

Please see below for some summary statistics of the international stock indexes.

```{r, results='asis'}
# generate log returns
lret = apply(log(index_d), 2, diff)

# summarize data
descr <- describe(lret)
descr <- descr[, c("n", "mean", "sd", "median", "min", "max", "skew", "kurtosis")]

kable(descr)
```

## Autocorrelation of international stock indexes

This answers Part 1BQ1.

### ACF and PACF Background

Below we plot the **autocorrelation functions (ACF)** and partial **autocorrelation functions (PACF)** of each series with 20 lags. The blue line indicates the 95% confidence level of the coefficients.

For each lag period $k$, the **ACF** plot shows the autocorrelation of $y_t$ and $y_{t+k}$. The significance of the ACF coefficients reveals whether $y_t$ exhibits behavior of an **autoregressive (AR)** process.

For each lag period $k$, the **PACF** plot shows the the autocorrelation of series $z_t$ and $z_{t+k}$ with the linear dependence of $z_t$ on $z_{t+1}, z_{t+2}, …, z_{t+k}$ removed. The significance of the PACF coefficients tell reveals whether $y_t$ exhibits behavior of a **moving average (MA)** process.

### ACF and PAC Results

The indices **DAXINDX**, **FRCAC40, NIKKEI,** and **SPCOMP** exhibit no autocorrelation as the lag coefficients on the ACF plots are mostly non-significant.

**HNGKNGI** and **SNGALLS** exhibit tailing off in the ACF plot. Then these series may be modeled with an AR model. Therefore, these series may be autocorrelated.

**FTSE100** exhibits some tailing off in the ACF and PACF plots, and may be modeled with an ARMA model. Therefore, this index may be autocorrelated.

```{r acf_pacf, results='asis'}

acf_tabs <- function(data, lag.max=20, plot=T){

  # create tables for ACF and PACF values
  acf_tab <- matrix(nrow=ncol(data), ncol=lag.max,
                    dimnames=list(index=colnames(data),
                                  lag=1:lag.max
                    )
  )
  pacf_tab <- matrix(nrow=ncol(data), ncol=lag.max,
                     dimnames=list(index=colnames(data),
                                   lag=1:lag.max)
  )
  
  for (c in colnames(data)){

    # data for each column removing na
    x <- data[!is.na(data[,c]), c]

    
    if (plot){
    # two columns for ACF and PACF
    par(mfcol=c(1, 2))
    }
    
    # plot ACf and PACF
    acf_val <- acf(x, main=c, plot=plot)
    pacf_val <- pacf(x, main=c, plot=plot)

    # save coefficients
    acf_tab[c, ] <- acf_val$acf[2:(lag.max+1)]
    pacf_tab[c, ] <- pacf_val$acf[1:lag.max]

  }

  return(list(acf=acf_tab, pacf=pacf_tab))

}

tabs = acf_tabs(lret)

# xtable(t(tabs$acf))
# xtable(t(tabs$pacf))

kable(t(tabs$acf))
kable(t(tabs$pacf))
```

## Ljung-Box Test

This part answers Part 1BQ2.

The Ljung-Box statistic is given by$$
Q_{LB}(k) = T(T+2) \sum_{j=1}^k \frac{\hat \rho^2}{T-j}
\sim \chi^2(k-p)
$$

which tests the null hypothesis of no autocorrelation,

$$\begin{align}
H_0 &: \rho_1 = \rho_2 = ... = \rho_k = 0. \\
H_1 &: \exists j \in \{1, 2, ..., k\}, \; \rho_j \ne 0.
\end{align}$$

We present the p-values of the Ljung-Box test for each index with $k \in \{10, 50, 100\}$ lags below, with degrees of freedom $d = k - 2$.

```{r ljungbox, results='asis'}
# Ljung-Box test function
LB <- function(data, lag, p){

  # time periods
  T <- length(data)

  # get ACF coeffs
  rho = acf(data, lag.max=lag, plot=F)$acf

  # remove 0th lag coeffs then square
  rho_sq = rho[2:(lag+1)]**2

  # test statistic
  Q = T * (T+2) * sum(rho_sq / (T-1:lag))

  # return test and p-value
  return(list(test=Q, pval=1-pchisq(Q, df=lag-p)))
}


# lag periods to test
lags <- c(10, 50, 100)

# degrees of freedom df = lag - p
# p is number of parameters estimated
p <- 0

# table of LB test statistics
LB_tests <- matrix(nrow=length(lags), ncol=ncol(lret),
                  dimnames=list(lag=lags, index=colnames(lret))
                  )

# table of Chi-square test p-values
LB_pvals <- matrix(nrow=length(lags), ncol=ncol(lret),
                   dimnames=list(lag=lags, index=colnames(lret))
                   )

# run Ljung-Box tests
for (c in colnames(lret)){

  for (i in 1:3){

    # remove na from data
    x <- lret[!is.na(lret[,c]), c]
    LB_res <- LB(x, lag=lags[i], p)

    # significance level stars
    pval <- signif(LB_res$pval, 3)
    for (qt in c(0.1, 0.05, 0.01)){
      if (LB_res$pval < qt){
        pval <- paste(pval,'*', sep='')
      }
    }

    # save test stat and pvals
    LB_tests[i, c] <- LB_res$test
    LB_pvals[i, c] <- pval

  }
}


comment <- paste('This table presents p-values of',
                 'Ljung-Box tests of no autocorrelation.',
                 'Significance levels:',
                 '\\* p-value < 0.1,',
                 '\\** p-value < 0.5,',
                 '\\*** p-value <0.01.')

kable(LB_pvals, caption=comment)

# LB_tests <- list(LB_tests)
# attr(LB_tests, "message") <- c(
#                   'This table presents p-values of Ljung-Box tests of no autocorrelation.',
#                  'Significance levels:',
#                  '* p-value < 0.1,',
#                  '** p-value < 0.5,',
#                  '*** p-value <0.01.'
#                  )
# 
# print(
#  xtable(LB_pvals, caption="Table of chi-square p-values")
#       , caption.placement = "top"
#       , sanitize.text.function = identity
#       )

```

From the p-value of the test results, for all lag orders $k \in \{10, 50, 100\}$ we can reject the null of no autocorrelation for the **FTSE100, HNGKNGI, NIKKEI, SNGALLS,** and **SPCOMP** at less than the 1% quantile level of the Chi-squared distribution. Therefore, there is some strong evidence of autocorrelation in these indices.

For **DAXINDX,** we can reject no autocorrelation with $k=50$ lags at the 5% level with $k = 100$ lags at the 5% quantile level of the Chi-squared distribution. There is some evidence that the DAX is auto-correlated, but only at high lag orders.

For **FRCAC40**, we cannot reject no autocorrelation at any lags $k \in \{10, 50, 100\}$ at the 10% quantile level. Therefore, there is little evidence of autocorrelation in the FRCAC40 index.

## Cross-correlations

```{r corr_mat, results='asis'}
corr_mat <- function(data, lag=1) {
  # column names
  cols <- colnames(data)

  # correlation matrix
  corr_mat <- matrix(nrow = ncol(data), ncol = ncol(data),
                     dimnames=list(lags=cols, cols))

  for (c1 in cols){
    for (c0 in cols){
      # periods with either are NA
      isna <- (is.na(data[, c1]) | is.na(data[, c0]))

      # non-na returns of pair
      pair_data <- data[!isna, c(c1, c0)]
      T <- nrow(pair_data)

      # add period lag autocorrelation to matrix
      corr_mat[c1, c0] <- cor(pair_data[1:(T-lag),c1], pair_data[(1+lag):T,c0])

      # acf(pair_data)
      # pacf(pair_data)
    }
  }

  # re-label past/current period returns
  rownames(corr_mat) <- paste(cols, '(t-1)', sep='')
  colnames(corr_mat) <- paste(cols, '(t)', sep='')

  return(corr_mat)

}

kable(corr_mat(lret, lag=0))
kable(corr_mat(lret, lag=1))
```

## Squared log returns

This subsection answers Part 1BQ4

```{r sq_lret, results='asis'}
sq_lret = lret^2
```


## Question 4
```{r , results='asis'}

```
