---
title: "Report for PS 1"
author:
- Jack Xie
- Rebecca Car
- Kazi Jahurul Islam
date: ""
header-includes:
   - \usepackage{bbm}
output:
  pdf_document:
    keep_tex: yes
  df_print: kable
  html_document:
    df_print: paged
toc: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library("FE")
library(psych)
library(kableExtra)
```



#  Asset Return Predictability and Market Efficiency

## Testing for asset return predictability

In this part of the report we are going to discuss the test for asset return predictability based on autocorrelation functions, Ljung-Box statistics and variance ratio tests using the \textbf{Dow Jones Daily} and \textbf{Dow Jones Weekly} data set.


```{r, echo=FALSE}
############## Task 1. #################
logreturn_DJ_d = DJ_d$r_Dow_Jones[!is.na(DJ_d$r_Dow_Jones)]
logreturn_DJ_w = DJ_w$r_close[!is.na(DJ_w$r_close)]
par(mfrow=c(2,2))
# ACF and PACF values of daily data
acf(logreturn_DJ_d, main = "ACF of daily Dow Jones returns")
pacf(logreturn_DJ_d, main="PACF of daily Dow Jones returns")

# ACF and PACF values of weekly data
acf(logreturn_DJ_w, main = "ACF of Weekly Dow Jones returns")
pacf(logreturn_DJ_w, main="PACF of weekly Dow Jones returns")
```

In the above figures we observe significant lags from the \textbf{ACF} and \textbf{PACF} plot for both \textbf{Dow Jones Daily} and \textbf{Dow Jones Weekly} data. Which is the indication of autocorrealatios. 

Now at this point we are going to apply Lung-Box and variance ratio test to check autocorrelation for both data set. The results are presented below:





























